
## Overview

dsapptools gives Datasketch a compendium of useful and generic functions in order to improve shiny apps developing.


## Installation

Install the development version of dsapptools from GitHub with:

``` r
# install.packages("devtools")
remotes::install_github("datasketch/dsapptools")
```

## Usage

Some of the main functions of this package are:

- Row filtering with `data_filter()`:

```{r}
library(dsapptools)

# Dataset
data <- iris

# Create a homodatum dictionary
dic <- homodatum::create_dic(data)
names(data) <- dic$id

# Create a list and set the column and the rows that must be kept
var_inputs <- list("species" = c("versicolor"))

# Apply filter
data_result <- data_filter(data,
                           dic,
                           var_inputs)

# Check
unique(data_result$species)
```


- Column(s) selection with `variable_selection`

```{r}
# Dataset
data <- iris

# Select variables
data_result <- variable_selection(data = data,
                                  viz = NULL,
                                  path = NULL,
                                  "Sepal.Length", "Petal.Length")

# Check
names(data_result)
```

- Make some standard calculations with `var_aggregation`

```{r}
library(homodatum)

# Dataset
data <- homodatum::sample_data("Cat-Cat-Num-Num-Cat")
names(data) <- c("a", "b", "c", "d", "e")

# Create a dataset dictionary
dic <- create_dic(data)
names(data) <- dic$id

# Count the number of apperences for each category combination from the dataset
data_result <- var_aggregation(data = data,
                               dic = dic,
                               agg = "count",
                               to_agg = "c",
                               name = "Conteo",
                               group_var = c("a", "b"))
```

- Get a proper visualization from the `lfltmagic` package with `viz_selection()`

```{r}
# Dataset
data <- iris

# Create a dataset dictionary
dic <- homodatum::create_dic(data)
names(data) <- dic$id

# Make some calculation
data_viz  <- var_aggregation(data,
                             dic, agg = "count",
                             group_var = "species",
                             to_agg = "species",
                             name = "Total")

# Get the proper visualization
viz_result <- viz_selection(data = data_viz,
                            dic = dic,
                            viz = "map", 
                            num_hType = TRUE)

viz_result
```



